\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-06-15 paper.qmd
Update choice of bins

<!--add three choice of bins 3, 10, 34-->

```{r}
## Hexagonal binning to have regular hexagons
hb_obj_scurve1 <- hex_binning(
  data = umap_scurve_scaled, 
  bin1 = 3, 
  r2 = r2)

@@

```{r}
## Hexagonal binning to have regular hexagons
hb_obj_scurve2 <- hex_binning(
  data = umap_scurve_scaled, 
  bin1 = 10, 
  r2 = r2)

@@

```{r}
## Hexagonal binning to have regular hexagons
hb_obj_scurve3 <- hex_binning(
  data = umap_scurve_scaled, 
  bin1 = 34, 
  r2 = r2)

@@

```{r}
#| echo: false
#| label: fig-bins-scurve
#| fig-pos: H
#| fig-cap: "Hexbin plots from different number of bins for the UMAP applied to S-curve data: (a) $b = 15$ (3, 5), (b) $b = 190$ (10, 19), and (c) $b = 2176$ (34, 64). The hexbins are colored based on the density of points, with darker colors indicating higher density and yellow color representing lower density within each bin. What is the number of bins that would be effective?"
#| fig-width: 6
#| fig-height: 3

>>>>

<!--add three choice of bins 7, 10, 14-->

```{r}
## Hexagonal binning to have regular hexagons
hb_obj_scurve1 <- hex_binning(
  data = umap_scurve_scaled, 
  bin1 = 7, 
  r2 = r2,
  q = 0.05)

@@

```{r}
## Hexagonal binning to have regular hexagons
hb_obj_scurve2 <- hex_binning(
  data = umap_scurve_scaled, 
  bin1 = 10, 
  r2 = r2,
  q = 0.05)

@@

```{r}
## Hexagonal binning to have regular hexagons
hb_obj_scurve3 <- hex_binning(
  data = umap_scurve_scaled, 
  bin1 = 14, 
  r2 = r2,
  q = 0.05)

@@

```{r}
#| echo: false
#| label: fig-bins-scurve
#| fig-pos: H
#| fig-cap: "Hexbin plots from different number of bins for the UMAP applied to S-curve data: (a) $b = 91$ (7, 13), (b) $b = 190$ (10, 19), and (c) $b = 364$ (14, 26). The hexbins are colored based on the density of points, with darker colors indicating higher density and yellow color representing lower density within each bin. What is the number of bins that would be effective?"
#| fig-width: 6
#| fig-height: 3

### 2024-06-15 paper.tex
S-curve explanation
Update choice of bins

To illustrate the method, we use \(7\text{-}D\) simulated data, which we
call the ``S-curve''. It is constructed by setting
\(X_1 = \sin(a), X_2 = U(0, 2), X_3 = \text{sign}(a) \times (\cos(a) - 1), \forall a \in [-3\pi/2, 3\pi/2]\).
The remaining variables \(X_4, X_5, X_6, X_7\) are all uniform error,
with small variance. We would consider \(T=(X_1, X_2, X_3)\) to be the
true model.

@@

\caption{\label{fig-bins-scurve}Hexbin plots from different number of
bins for the UMAP applied to S-curve data: (a) \(b = 15\) (3, 5), (b)
\(b = 190\) (10, 19), and (c) \(b = 2176\) (34, 64). The hexbins are
colored based on the density of points, with darker colors indicating
higher density and yellow color representing lower density within each
bin. What is the number of bins that would be effective?}

>>>>

To illustrate the method, we use \(7\text{-}D\) simulated data, which we
call the ``S-curve''. It is constructed by simulating \(n=750\)
observations from \(\theta \sim U(-3\pi/2, 3\pi/2)\),
\(X_1 = \sin(\theta)\), \(X_2 \sim U(0, 2)\) (adding thickness to the
S), \(X_3 = \text{sign}(\theta) \times (\cos(\theta) - 1)\). The
remaining variables \(X_4, X_5, X_6, X_7\) are all uniform error, with
small variance. We would consider \(T=(X_1, X_2, X_3)\) to be the
geometric structure (true model) that we hope to capture.

@@

\caption{\label{fig-bins-scurve}Hexbin plots from different number of
bins for the UMAP applied to S-curve data: (a) \(b = 91\) (7, 13), (b)
\(b = 190\) (10, 19), and (c) \(b = 364\) (14, 26). The hexbins are
colored based on the density of points, with darker colors indicating
higher density and yellow color representing lower density within each
bin. What is the number of bins that would be effective?}
